### 2021-10-28 manuscript/hiv-gwas.tex

\begin{figure}[H]
	\begin{center}
		\includegraphics[width=0.7\linewidth]{figures/model_figure}
		\caption{A statistical model of the spVL trait. The virus-determined part of spVL, $g_v$, evolves according to an OU process along the viral phylogeny. The dashed line shows the evolutionarily optimal trait value $\theta$. The environmentally-determined part of spVL, $e$, including direct host genetic effects and other environmental effects, is modeled as a Gaussian random variable whose value is added at the tips of the phylogeny.}
		\label{fig:spVLModel}
	\end{center}
\end{figure}

>>>>

\begin{figure}[H]
	\begin{center}
		\includegraphics[width=0.6\linewidth]{figures/model_figure}
		\caption{A statistical model of the spVL trait. (A) The virus-determined part of spVL, $g_v$, evolves according to an OU process along (C) the viral phylogeny. The dashed line in (A) shows the expected value of the trait at each point in time. (B) The environmentally-determined part of spVL, $e$, including host genetic effects, interaction effects, and other environmental effects, is modeled as a Gaussian random variable whose value is independently drawn for each host at the tips of the phylogeny.}
		\label{fig:spVLModel}
	\end{center}
\end{figure}
